Why shouldn't you use numerical tests to diagnose the linear regression models?

### 2022-04-26 paper_comparison/paper_comparison/paper_comparison.Rmd
update test

Diagnostics of the classical normal linear regression model conventionally involve evaluating the fitness of the proposed model, detecting the presence of influential observations and outliers, checking the validity of model assumptions and many more. Tools such as summary statistics, hypothesis testing, and data plots are essential for a systematic and detailed examination of the regression model [@mansfield1987diagnostic].

## Data plots

Data plots are one of the most important and preferred methods of regression diagnostics. Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are refereed to as standard residual plots. They are commonly used to identify patterns which are indicative of nonconstant error variance or nonlinearity [@cook1982residuals]. Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used always present. While raw residuals are the most common output of computer regression software package, by applying a scaling factor, the ability of revealing nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst2018regression].

@@

Other types of data plots that are often used in regression diagnostics include partial residual plots and probability plots. Partial residual plots are useful supplements to standard residual plots as they provide additional information on the direction of linearity as well as the nonlinearity of each predictor. Probability plots can be used to compare the sampling distribution of the residuals to the normal distribution.

@@

>>>>

Regression diagnostics conventionally involve evaluating the fitness of the proposed model, detecting the presence of influential observations and outliers, checking the validity of model assumptions and many more. Common diagnostic techniques including summary statistics, hypothesis testing, and data plots are essential tools for a systematic and detailed examination of the regression model [@mansfield1987diagnostic].

## Diagnostic plots

Regression analysis is a field of study with at least a hundred years of history. Many of those regression diagnostic methods and procedures are mature and well-established in books first published in the twentieth century, such as @draper_applied_2014, @montgomery_introduction_2012, @belsley_regression_1980, @cook_applied_1999 and @cook1982residuals. Regardless of the level of difficulty of the book, one will find the importance and usefulness of diagnostic plots being emphasized again and again. Checking diagnostic plots is also the recommended starting point for validating model assumptions like normality, homoscedasticity and linearity [@anscombe_examination_1963].

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are refereed to as standard residual plots. They are commonly used to identify patterns which are indicative of nonconstant error variance or non-linearity [@cook1982residuals]. Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used always present. While raw residuals are the most common output of computer regression software package, by applying a scaling factor, the ability of revealing nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst2018regression].

@@

Other types of data plots that are often used in regression diagnostics include partial residual plots and probability plots. Partial residual plots are useful supplements to standard residual plots as they provide additional information on the extent of the non-linearity. Probability plots can be used to compare the sampling distribution of the residuals to the normal distribution for assessing the normality assumptions.

@@

In addition to diagnostic plots, researcher may also perform formal tests for detecting model defects. Depends on the alternative, variety of tests can be applied. For example, for testing heteroskedasticity, 
one may use the White test [@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [@breusch_simple_1979]. And for testing non-linearity, there are RESET test [@ramsey_tests_1969] and F-test.

As discussed in @cook1982residuals, most residual based tests for a particular type of departures from model assumptions are sensitive to other types of departures. Especially, outliers will often  incorrectly trigger the rejection of null hypothesis despite the residuals are well-behaved [@cook_applied_1999]. This can be largely avoided in diagnostic plots as experienced analysts can evaluate the acceptability of assumptions flexibly, even in the presence of outliers. Furthermore, @montgomery_introduction_2012 stated that based on their experience, statistical tests are not widely used in regression diagnostics. Most importantly, the same or even larger amount of information can be provided by diagnostic plots than the corresponding tests in most empirical studies. But still, the effectiveness of statistical tests shall not be disrespected. Statistical tests have chance to provide analysts with unique information. There are also situations where no suitable diagnostic plots can be found for a particular violation of the assumptions, or excessive diagnostic plots need to be checked. One will have no choice but to rely on statistical tests if there is any. A good regression diagnostic practice should be a combination of both methods.

## Visual inference

Diagnostic plots are

However, unlike confirmatory data analysis built upon rigorous statistical procedures, e.g., hypothesis testing, visual diagnostics relies on graphical perception - human’s ability to interpret and decode the information embedded in the graph [@cleveland_graphical_1984], which is to some extent subjective. Further, visual discovery suffers from its unsecured and unconfirmed nature where the degree of the presence of the visual features typically can not be measured quantitatively and objectively, which may lead to over or under-interpretations of the data. One such example is finding an over-interpretation of the separation between gene groups in a two-dimensional projection from a linear discriminant analysis when in fact there are no differences in the expression levels between the gene groups and separation is not an uncommon occurrence [@roy_chowdhury_using_2015].

Recently, a new branch of statical inference

Visual inference was first introduced in a 1999 Joint Statistical Meetings (JSM) talk with the title "Inference for Data Visualization" by @buja_inference_1999 as an idea to address the issue of valid inference for visual discoveries of data plots [@gelman_exploratory_2004]. Later, in the Bayesian context, data plots was systematically considered as model diagnostics by taking advantage of the data simulated from the assumed statistical models [@gelman_bayesian_2003; @gelman_exploratory_2004].

### 2022-04-26 paper_comparison/paper_comparison/paper_comparison.tex
update test

\begin{keywords}
Sections; lists; figures; tables; mathematics; fonts; references;
appendices
\end{keywords}

@@

Diagnostics of the classical normal linear regression model
conventionally involve evaluating the fitness of the proposed model,
detecting the presence of influential observations and outliers,
checking the validity of model assumptions and many more. Tools such as
summary statistics, hypothesis testing, and data plots are essential for
a systematic and detailed examination of the regression model
\citep{mansfield1987diagnostic}.

\hypertarget{data-plots}{%
\subsection{Data plots}\label{data-plots}}

Data plots are one of the most important and preferred methods of
regression diagnostics. Graphical summaries in which residuals are
plotted against fitted values or other functions of the predictor
variables that are approximately orthogonal to residuals are refereed to
as standard residual plots. They are commonly used to identify patterns
which are indicative of nonconstant error variance or nonlinearity
\citep{cook1982residuals}. Raw residuals and studentized residuals are
the two most frequently used residuals in standard residual plots. The
debt on which type of residuals should be used always present. While raw
residuals are the most common output of computer regression software
package, by applying a scaling factor, the ability of revealing
nonconstant error variance in standard residual plots will often be
enhanced by studentized residuals in small sample size
\citep{gunst2018regression}.

@@

\bibliographystyle{tfcad}
\bibliography{interactcadsample.bib}

>>>>

\begin{keywords}
visual inference; model diagnostics;
\end{keywords}

@@

Regression diagnostics conventionally involve evaluating the fitness of
the proposed model, detecting the presence of influential observations
and outliers, checking the validity of model assumptions and many more.
Common diagnostic techniques including summary statistics, hypothesis
testing, and data plots are essential tools for a systematic and
detailed examination of the regression model
\citep{mansfield1987diagnostic}.

\hypertarget{diagnostic-plots}{%
\subsection{Diagnostic plots}\label{diagnostic-plots}}

Regression analysis is a field of study with at least a hundred years of
history. Many of those regression diagnostic methods and procedures are
mature and well-established in books first published in the twentieth
century, such as \citet{draper_applied_2014},
\citet{montgomery_introduction_2012}, \citet{belsley_regression_1980},
\citet{cook_applied_1999} and \citet{cook1982residuals}. Regardless of
the level of difficulty of the book, one will find the importance and
usefulness of diagnostic plots being emphasized again and again.
Checking diagnostic plots is also the recommended starting point for
validating model assumptions like normality, homoscedasticity and
linearity \citep{anscombe_examination_1963}.

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are refereed to as standard residual plots. They
are commonly used to identify patterns which are indicative of
nonconstant error variance or non-linearity \citep{cook1982residuals}.
Raw residuals and studentized residuals are the two most frequently used
residuals in standard residual plots. The debt on which type of
residuals should be used always present. While raw residuals are the
most common output of computer regression software package, by applying
a scaling factor, the ability of revealing nonconstant error variance in
standard residual plots will often be enhanced by studentized residuals
in small sample size \citep{gunst2018regression}.

@@

In addition to diagnostic plots, researcher may also perform formal
tests for detecting model defects. Depends on the alternative, variety
of tests can be applied. For example, for testing heteroskedasticity,
one may use the White test
\citep{white_heteroskedasticity-consistent_1980} or the Breusch-Pagan
test \citep{breusch_simple_1979}. And for testing non-linearity, there
are RESET test \citep{ramsey_tests_1969} and F-test.

As discussed in \citet{cook1982residuals}, most residual based tests for
a particular type of departures from model assumptions are sensitive to
other types of departures. Especially, outliers will often incorrectly
trigger the rejection of null hypothesis despite the residuals are
well-behaved \citep{cook_applied_1999}. This can be largely avoided in
diagnostic plots as experienced analysts can evaluate the acceptability
of assumptions flexibly, even in the presence of outliers. Furthermore,
\citet{montgomery_introduction_2012} stated that based on their
experience, statistical tests are not widely used in regression
diagnostics. Most importantly, the same or even larger amount of
information can be provided by diagnostic plots than the corresponding
tests in most empirical studies. But still, the effectiveness of
statistical tests shall not be disrespected. Statistical tests have
chance to provide analysts with unique information. There are also
situations where no suitable diagnostic plots can be found for a
particular violation of the assumptions, or excessive diagnostic plots
need to be checked. One will have no choice but to rely on statistical
tests if there is any. A good regression diagnostic practice should be a
combination of both methods.

\hypertarget{visual-inference}{%
\subsection{Visual inference}\label{visual-inference}}

Diagnostic plots are

However, unlike confirmatory data analysis built upon rigorous
statistical procedures, e.g., hypothesis testing, visual diagnostics
relies on graphical perception - human's ability to interpret and decode
the information embedded in the graph \citep{cleveland_graphical_1984},
which is to some extent subjective. Further, visual discovery suffers
from its unsecured and unconfirmed nature where the degree of the
presence of the visual features typically can not be measured
quantitatively and objectively, which may lead to over or
under-interpretations of the data. One such example is finding an
over-interpretation of the separation between gene groups in a
two-dimensional projection from a linear discriminant analysis when in
fact there are no differences in the expression levels between the gene
groups and separation is not an uncommon occurrence
\citep{roy_chowdhury_using_2015}.

Recently, a new branch of statical inference

Visual inference was first introduced in a 1999 Joint Statistical
Meetings (JSM) talk with the title ``Inference for Data Visualization''
by \citet{buja_inference_1999} as an idea to address the issue of valid
inference for visual discoveries of data plots
\citep{gelman_exploratory_2004}. Later, in the Bayesian context, data
plots was systematically considered as model diagnostics by taking
advantage of the data simulated from the assumed statistical models
\citep{gelman_bayesian_2003, gelman_exploratory_2004}.

\bibliographystyle{tfcad}
\bibliography{paper.bib}
